\section{Motivation}
Working Memory (WM) is a general-purpose cognitive system responsible for temporary holding information in service of higher-order cognition
systems. Such a system, capable of recalling and holding previous stored information, is of fundamental importance for complex tasks as reasoning,
decision making and complex behaviour.

It is widely recognised that the Working Memory is located in the cortical structure of the Prefrontal cortex (PFC), although there is still no consensus
about the underlying neuronal mechanisms that regulates it.
Several abstract neurocomputational models, have been built on a particular neurobiological hypothesis, at different levels of abstraction, to account
for human experimental data on Working Memory.

In the model adopted in this thesis, Working Memory is encoded by fast and volatile Hebbian synaptic plasticity and modulated by non-Hebbian intrinsic excitability. Our non-spiking model belongs to a special family of biologically inspired recurrent Artificial Neural Network called Bayesian Confidence Propagation Neural Network (BCPNN).
To the best of our knowledge, the proposed dynamical recurrent neural network has never been studied from a control theory perspective. However,
considering the modular structure of the network and the dynamic evolution of the interactions of its units, control theory could provide systematic
approaches for a better understanding and analysis of such a system. In particular, this thesis gives a networked control representation of the network in order to analyse its stability properties and propose techniques to tune the parameters that characterise it.

\section{Previous work}


\section{Project outline}
\section{Attractor Neural Networks}
\input{text/intro/attractor_neural_newtork.tex}
\section{Bayesian Confidence Propagation Neural Networks}
